Continous time Markov chain models; \\ extension, simulation and visualisation

### 2015-02-09 Response.tex

\begin{itemize}

% 1a
\item {
{\it
\textbf{
Briefly described the evolutionary models, such as GY94, that are later used.
}% END: textbf
}% END: it
}% END: item
\\
Done, there is now a \emph{Markov models of codon evolution} section in the introductory chapter.

% 1b
\item {
{\it
\textbf{
Briefly described how to accommodate time-stamped sequences, which is now considered in the analyses in Chapter 2, but not really discussed.
}% END: textbf
}% END: it
}% END: item
\\
Done, see Subsection~\ref{sub:dated_trees}.

% 1c
\item {
{\it
\textbf{
Give a bit more detail on phylogeography, e.g. how do the models look like and what is the connection between phylogeography and epoch models (some connection is described in Chapter 2, but remains a bit vague).
}% END: textbf
}% END: it
}% END: item
\\
Done, I think that the figure and some extra explanations in Subsection~\ref{sub:phylogeo} should make it clear now.

@@

\end{itemize}

% 2
\item {
{\it
\textbf{
It is sometimes unclear in Chapter 2 whether the analysis is performed under a fixed evolutionary tree or not. 
This is especially so in the evaluation of Bayes Factors in Table 2.3. 
It would also have been nice to understand better whether the use of the epoch model (versus not) has an essential impact on tree reconstruction. 
Somewhat related, it would have been nice to learn from the simulation study how mislead one could be if the data were generated under an epoch model, but analyzed under a simpler model. 
I am not asking for additional analyses here, but merely for additional clarification or insight.
}% END: textbf
}% END: it
}% END: item
\\
% FB: I don't get the first part of this comment. In the Intro we clearly write:
% "Our Bayesian approach also does not condition on a fixed tree topology but averages over all plausible evolutionary histories." (p 46) \\
% PL: OK, but to make it even more explicit I have added this to the results section (in simulation results): 'In all our analyses of the replicate data, as well as in the analyses of the real-world data sets in the next sections, we consider the tree as random and estimate it from the nucleotide data.' (this still needs to be tagged).
To re-iterate the fact that our model does not condition on a known tree topology we now write:

\begin{quote}
\myeditsvtwo
\end{quote}

We now also entertain a number of simulations which asses the impact of correcting for time-heterogeneity on tree reconstruction. 
The simulations are running, I will discuss them during the presentation.

@@

% 7
\item {
{\it
\textbf{
If I am right that matrix P(t) on the bottom of page 22 is four-dimensional, then why not write it in full, which will be less confusing?
}% END: textbf
}% END: it
}% END: item
\\
Corrected.

% 8
\item {
{\it
\textbf{
P25, the statement at the end of the penultimate paragraph (`most plausible hypothesis for the data') is vague.
}% END: textbf
}% END: it
}% END: item
\\
This statement now reads:

\begin{quote}
\myeditsveight
\end{quote}

% 9
\item {
{\it
\textbf{
P28, I understand what T(n) is, but would nevertheless find it helpful if it were stated more explicitly.
}% END: textbf
}% END: it
}% END: item
\\
% FB: I don't understand the question in the definition we clearly define T as being simply a function on a positive subset of real numbers?
% Does he mean we should wrote "time"? but this is not always true?
% PL: OK, but can we then state something like this: T(n) can be interpreted as time in most practical situations, but this does necessarily need to be the case, e.g.....?
Done, I now call it the ``worst case time'' scenario.

@@

% 9
\item {
{\it
\textbf{
The bibliography would have been be easier to consult if last names came first than the initials, as usual.
}% END: textbf
}% END: it
}% END: item
\\
Corrected.

% 10
\item {
{\it
\textbf{
Page 137: Figure B.12 should be in color. 
Otherwise it is very difficult to grasp.
}% END: textbf
}% END: it
}% END: item
\\
Corrected, all the figures presenting SPREAd output are now in color.

% 11
\item {
{\it
\textbf{
Page 140: Figure B.13 should be in color. 
Otherwise it is very difficult to grasp.
}% END: textbf
}% END: it
}% END: item
\\
Corrected, all the figures presenting SPREAd output are now in color.

% 12
\item {
{\it
\textbf{
Page 143: Figure B.15 should be in color. 
Otherwise it is very difficult to grasp.
}% END: textbf
}% END: it
}% END: item
\\
Corrected, all the figures presenting SPREAD output are now in color.

### 2015-02-09 chapters/chapter01.tex
implementing comments

% \noindent
In other words $T(n)$ is $\mathcal{O}\left(f(n)\right)$ if and only if for all sufficiently large input values $T(n)$ is bounded from above by some constant multiple of $f(n)$.
This makes the Big-O notation useful when analyzing algorithms for run-time efficiency and makes it possible to, for example, compare routines without the added overhead of negligible terms, such as the architecture at which the code was run, the choice of language or compiler.
We will now briefly discuss some of the most common serial computational orders and their examples.

>>>>

% \noindent
In other words $T(n)$, which can be interpreted as the ``worst-case'' time complexity of an algorithm,
% Since an algorithm's performance time may vary with different inputs of the same size
is $\mathcal{O}\left(f(n)\right)$ if and only if for all sufficiently large input values $T(n)$ is bounded from above by some constant multiple of $f(n)$.
This makes the Big-O notation useful when analyzing algorithms for run-time efficiency and makes it possible to, for example, compare routines without the added overhead of negligible terms, such as the architecture at which the code was run, the choice of language or compiler.
We will now briefly discuss some of the most common serial computational orders and their examples.

### 2015-02-09 chapters/chapter02.tex
implementing comments

Figure~\ref{fig:collapsing} illustrates this action for a branch that spans a single boundary at $T_1$ with $\mathbf{Q}_1$ governing the process before the boundary and $\mathbf{Q}_2$ after the boundary. Letting $X(T_1) = k$ represent the augmented state of the stochastic process at the boundary, we compute

>>>>

Figure~\ref{fig:collapsing} illustrates this action for a branch that spans a single boundary at knwon time $T_1$ with $\mathbf{Q}_1$ governing the process before the boundary and $\mathbf{Q}_2$ after the boundary. Letting $X(T_1) = k$ represent the augmented state of the stochastic process at the boundary, we compute
